---
title: "visit_scotland_cleaning"
output: html_notebook
---
# Librarys
```{r}
library(tidyverse)
library(tidyr)
library(janitor)
library(dplyr)
library(here)
library(lubridate)
```

# Read in the data and run clean names
```{r}
regional_domestic_tourism <- read_csv("data/regional_domestic_tourism.csv") %>%  clean_names()
scot_accomodation_occupancy <- read_csv("data/scottish_accomodation_occupancy.csv") %>%  clean_names()
day_visits_activities <- read_csv("data/tourism_day_visits_activities.csv") %>%  clean_names()
day_visits_demographics <- read_csv("data/tourism_day_visits_demographics.csv") %>%  clean_names()
day_visits_location <- read_csv("data/tourism_day_visits_location.csv") %>%  clean_names()
day_visits_transport <- read_csv("data/tourism_day_visits_transport.csv") %>%  clean_names()
```
Explore the data
```{r}
regional_domestic_tourism %>%
  head()
```

```{r}
scot_accomodation_occupancy %>% 
  head()
```

```{r}
day_visits_activities %>% 
  head()
```

```{r}
day_visits_demographics %>% 
  head()
```

```{r}
day_visits_location %>% 
  head()
```

```{r}
day_visits_transport %>% 
  head()
```

# clean the indiviudal data sets
# day_visits_activ cleaning
```{r}
day_visits_activities <- day_visits_activities %>% 
  select(-c(measurement, feature_code, breakdown_of_domestic_tourism)) #remove measurement column,feature code and breakdown

day_visits_activities <- day_visits_activities %>% #seperate visits and expendature into seperate columns
  pivot_wider(names_from = units,
              values_from = value)

day_visits_activities <- day_visits_activities %>% clean_names()
```

#day_visits_demo cleaning
```{r}
day_visits_demographics <- day_visits_demographics %>% 
  select(-c(measurement, feature_code, breakdown_of_domestic_tourism)) #remove measurement column, feature_code and breakdown

day_visits_demographics <- day_visits_demographics %>% #separate visits and expendature
  pivot_wider(names_from = units,
              values_from = value)
```

#day_visits_local cleaning
```{r}
day_visits_location <- day_visits_location %>% 
  select(-c(measurement, feature_code, breakdown_of_domestic_tourism)) #remove measurement column, feature code and breakdown

day_visits_location <- day_visits_location %>% #separate visits and expendature
  pivot_wider(names_from = units,
              values_from = value)
```

#regional_dom_tour cleaning
```{r}
regional_domestic_tourism <- regional_domestic_tourism %>% 
  select(-c(measurement, date_code, feature_code)) #remove measurement column, date code and feature code

#regional_domestic_tourism <- regional_domestic_tourism %>% killlll meeeeeeeeee
  #pivot_wider(names_from = units,
              #values_from = value)
```

#scot_accom_occ cleaning
```{r}
scot_accomodation_occupancy <- scot_accomodation_occupancy %>% 
  select(-c(measurement, units, feature_code)) #remove measurement, unit column and feature code
```

#day_visits_tran cleaning
```{r}
day_visits_transport <- day_visits_transport %>% 
  select(-c(measurement, feature_code, breakdown_of_domestic_tourism)) # remove measurement, feature code and breakdown

day_visits_transport <- day_visits_transport %>%
  pivot_wider(names_from = units,
              values_from = value)
```


# left join the activitys and demographics together by feature_code
```{r}
#day_visits_activity_demographic <- left_join(day_visits_activ, day_visits_demo, by = "feature_code")

#day_visits_activity_demographic
```
# left join the table together by feature_code

```{r}
#day_visits_location_transport <- left_join(day_visits_loca, day_visits_trans, by = "feature_code")

#day_visits_location_transport
```
# try not to explode laptop with a join
```{r}
#left_join(day_visits_activity_demographic, day_visits_location_transport, by = "feature_code")
```

when you open this back up, clean the data sets of variables before trying joining again